### Section, subsection, subsubsections

You can use `#`, `##`, `###` at the beginning of the line to define sections, subsections, and subsubsections.

```{r eval = F}
# This becomes section title

## This becomes subsection title

### This becomes subsubsection title
```

:::{.callout-note}
+ Confirm that `# Materials and Methods` and `## Data` in **sample_to_word.rmd** turn into a section and subsection title in **sample_to_word.docx**.
+ Note also that the sections and subsections are automatically numbered because `number_sections: true` in the YAML header.
:::

---

### Footnote

You can add a footnote using `^[]` like this:

```{r eval = F}
regular texts^[this is a footnote]
```

Footnotes are automatically numbered.

:::{.callout-note}
See the **Conclusion** section of **sample_to_word.rmd** and **sample_to_word.docx**. 
:::

---

### Line and page break

You can create a line break by inserting the following.

```markdown
<br>
```

:::{.callout-tip}
+ If `<br>` is placed in the same line as the one after which you want a break, then it does not give you a line break. Rather, put `<br>` in the next line.
+ Confirm this by inspecting the Materials and Methods section of the sample rmd and word files.
:::

To break a page, use
```{r, eval = F}
`r run_pagebreak()`
```

:::{.callout-note}
Confirm this by inspecting the end of the Introduction section of the sample rmd and word files.
:::


### List

You can create an unordered list by simply using either +, -, or * in front of each item. For example,

````{verbatim}
+ item 1
+ item 2
+ item 3
````

would print as below in the output WORD file.

+ item 1
+ item 2
+ item 3

You can create a nested list like below

````{verbatim}
+ item 1
  - item 1.1
  - item 1.2
+ item 2
+ item 3
````

would print as below in the output WORD file.

+ item 1
  - item 1.1
  - item 1.2
+ item 2
+ item 3

Here is an ordered list. 

````{verbatim}
1. item 1
2. item 2
3. item 3
````

1. item 1
2. item 2
3. item 3

### Bold and Italic

+ bold font: `**this becomes bold**` (or `__this becomes bold__`)
+ italic font: `*this becomes italic*` 

:::{.callout-note}
Confirm these by comparing the first sentence in the Introduction section of the sample rmd and WORD files.
:::