---
title: "Paper Title"
output: 
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
csl: pnas.csl
author: |
  | Author 1^[Corresponding author: email@email.com] $^1$, Author 2 $^1$, Author 3 $^2$
  | $^1$Affiliation1,  $^2$Affiliation2

abstract: |
  Your abstract goes here...

bibliography: bibliography.bib

fontsize: 12pt
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{setspace}\doublespacing
  \usepackage{lineno}
  \linenumbers
---

```{r include = F}
library(knitr)

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = FALSE,
  message = FALSE,
  cache = FALSE,
  echo = FALSE
)
```

```{r packages, include = F}
library(patchwork)
library(flextable)
library(officer)
library(modelsummary)
library(tidyverse)
```

```{r data-preparation, include = F}
#--- read the regression data ---#
reg_data <-
  readRDS("reg_data.rds") %>%
  .[, Zone := case_when(
    tgt_comb == "36-124" ~ "Zone 3",
    tgt_comb == "34-134" ~ "Zone 2",
  )] %>%
  filter(!is.na(Zone))
```

# Introduction

The issue this article addresses is **super** *important*!

-   **author names and year**: @schlenker2009nonlinear examined ....

-   **author names and year in parentheses**: [@schlenker2009nonlinear]

-   **multiple citations in parentheses**: [@schlenker2009nonlinear; @mas1995microeconomic]

-   **only year in parentheses**: [-@schlenker2009nonlinear]

<!-- page break -->

\newpage

# Materials and Methods

## Data

```{r}
#--- number of observations by zone ---#
num_obs <-
  reg_data %>%
  group_by(Zone) %>%
  summarize(n = n())

num_obs_z2 <- filter(num_obs, Zone == "Zone 2")$n
num_obs_z3 <- filter(num_obs, Zone == "Zone 3")$n
```

The number of observations are `r num_obs_z2` and `r num_obs_z3` for Zones 2 and 3, respectively.

Table \@ref(tab:sum-stat) presents summary statistics by zone.

## Statistical Model

```{=tex}
\begin{equation}
y = \beta_0 + \beta_1 x + \varepsilon (\#eq:eqn1)
\end{equation}
```

See equation \@ref(eq:eqn1).

---

```{=tex}
\begin{equation}
y = \beta_0 + \beta_1 x + \varepsilon \label{eq-tex}
\end{equation}
```

Refering to Equation (\ref{eq-tex}) in a Latex way.

---

```{=tex}
\begin{align}
Y_z & = f_z(S) + g_z(N) + h_z(X,Y) + \varepsilon_z (\#eq:al-eqn1) \\
& = \sum_{i=1}^k \phi_k(S) + g_z(N) + h_z(X,Y) + \varepsilon_z (\#eq:al-eqn2)
\end{align}
```

Refering to equation lines \@ref(eq:al-eqn1) and \@ref(eq:al-eqn2).

---

```{=tex}
\begin{align}
Y_z & = f_z(S) + g_z(N) + h_z(X,Y) + \varepsilon_z \notag \\
& = \sum_{i=1}^k \phi_k(S) + g_z(N) + h_z(X,Y) + \varepsilon_z (\#eq:al-second)
\end{align}
```

Equation \@ref(eq:al-second) is the second line.

Equation number for the first line is suppressed.

---

Our target coefficient is $\beta_1$ (in-line math).

# Results and Discussions

Table \@ref(tab:table-1) presents the regression results.

Figure \@ref(fig:fig-1) presents the distribution of yields by zone.

# Conclusions

bluh bluh[^1], another bluh bluh[^2]

[^1]: This is a footnote

[^2]: This is the second footnote

\newpage

# Tables

```{r sum-stat}

#--- find observations ---#
# write the function that forces the number of observations to be presented as integers
get_N <- function(x) {
  length(x) %>% as.integer()
}

library(kableExtra)

#--- create a summary table by zone ---#
summary_table <-
  reg_data %>%
  datasummary(
    Zone * (
      (`Yield (kg/ha)` = Yield) +
        (`Nitrogen Rate (kg/ha)` = aa_n) +
        (`Seed Rate (1000/ha)` = aa_s)
    ) ~
      Format(digits = 1) * get_N + Mean + SD + Min + Max,
    data = .,
    title = "Summary Statistics",
    output = "kableExtra"
  ) %>%
  kable_styling(latex_options = c("HOLD_position"))

summary_table
```


```{r regtable}
#| tbl-cap: Regression Results
#--- regressions ---#
lm_1 <- lm(mpg ~ hp + cyl, data = mtcars)
lm_2 <- lm(mpg ~ hp + cyl + wt, data = mtcars)

#--- create a regression results table ---#
modelsummary::modelsummary(
  list(lm_1, lm_2),
  title = "Regression Results",
  output = "latex"
) %>%
kable_styling(latex_options = c("HOLD_position"))

```

Summary statistics are presented in Table \@ref(tab:sum-stat). Regression results are presented in Table \@ref(tab:regtable).

\newpage

# Figures

I like Figure \@ref(fig:fig-1) a lot.

```{r fig-1, fig.cap = "The Distribution of Yield by Zone"}
ggplot() +
  geom_density(
    data = reg_data,
    aes(
      x = Yield,
      fill = Zone,
      alpha = 0.3
    )
  )
```

# References
