---
title: The Impact of Weather on Flight Delay
format: 
  pdf:
    toc: false
    number-sections: true
    number-depth: 2
    colorlinks: true
    keep-tex: true
    fontfamily: times
    fig-cap-location: bottom
    fig-align: center
    tbl-cap-location: top
    link-citations: true
    citecolor: red
    link-bibliography: true
    reference-location: document
    include-in-header:
      - preamble.tex
    template-partials: 
      - title.tex
author:
  - name: Forgot MyName
    email: johndoe@corps.com
    affiliations:
      - Random University
  - name: No Name
    affiliations:
      - Highest-ranked University
keywords:
  - Reproducible
  - R
date: "`r Sys.Date()`"
abstract: |
  Abstract: this research is so awesome that you cannot reject this paper.
keypoints:
  - qmd to pdf is pretty straightforward
  - no more key points
bibliography: bibliography.bib
csl: qje.csl
# csl: pnas.csl
---


```{r}
#| include: FALSE
#--- packages ---#
library(flextable)
library(officer)
library(modelsummary)
library(tidyverse)

#--- chunk options ---#
knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  messages = FALSE,
  warnings = FALSE
)
```


# Introduction

Nothing is more frustrating than flight delays. The goal of this article is to understand what weather variables affect flights delays so that we can control weather when such time comes in the future[^1].

[^1]: This is just for illustrating how to create a footnote

# Method

Regression analysis was used in this article. The econometric model writes as follows (equation \ref{econometric-model})):

\begin{align}
y_{i,t} = \beta_0 + \beta_1 temp_{i,t} + \beta_2 precip_{i,t} + \beta_3 wind_speed_{i,t} + v_{i,t} \lable{econometric-model}
\end{align}

## Code availability

All computations (including creating tables and plots) were conducted using R software [@R], The @fixest package was used to run regressions.

# Data

We use publicly available datasets from the R `nycflights13` package [@nycflights13]. @tbl-sum-stat presents the summary statistics.

```{r}
#| lable: tbl-sum-stat
#| tbl-cap: Summary Statistics
library(modelsummary)
reg_data <- readRDS(here::here("data/processed/reg_data.rds"))
modelsummary::datasummary(dep_delay + temp + precip + wind_speed ~ Mean + SD + Max, data = reg_data)
```

Figure @fig-hist-delay shows the histogram of departure delay by carrier for each of the airports. 

```{r}
#| lable: fig-hist-delay
#| fig-cap: Distribution of delay by carrier

knitr::include_graphics(here::here("results/figures/delay_box.pdf"))
```

# Results and Discussions

@tbl-reg-results presents the regression results.

```{r}
#| lable: tbl-reg-results
#| tbl-cap: Regression Results
reg_table <-
  readRDS(here::here("results/reg_results.rds")) %>%
  modelsummary(
    stars = TRUE,
    outpuy = "flextable",
    gof_omit = "IC|Log|Adj|F|Pseudo|Within|RMSE"
  )
reg_table
```

# Conclusion

Weather matters.

# References {-}

::: {#refs}
:::
